{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-03 bmvc_review.tex
Revised the body a bit.

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm would be economically and
practically, very attractive for any mobile, unmanned robotic
solutions on real-world applications. To make such pipelines more
realistic, however, those algorithms should run faster with small
footprint of computation resource consumption. To make an object
tracking algorithm with these practical requirements available, we
proposed an extension of KCF that essentially deploys three KCFs, in
turn, to address the scale change and dynamic maneuvers of a
target. The way we ran three KCFs in a harmonious way optimal in a
sense that efficiently handled the scale change and effectively
learned the translation of the target. However, by doing so, our
algorithm may introduce any potential drifts. To prevent this from
happening, we developed a Bayes filter, particle filter, to smooth the
transition between three KCFs. In particular, the particle filter
estimated the target's pixel coordinates using information about the
target's motion observed over frames. We used two publicly available
dataset to evaluate the performance of the proposed algorithm and
found that the performance of ours are 70.10\% for precision on 20
pixels and 53.00\% for success rate for OTB100 data, and 54.50\% and
40.2\% for UAV123 data. On average our method outperformed the
existing ones over 5\% on precision on 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123. 
%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version

>>>>

%\begin{figure}[!h]
%\centering
%\begin{tabular}{cc}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Precision_OTB100.pdf}}
%\bmvaHangBox{\includegraphics[width=2.50cm]{./figures/Success_OTB100.pdf}}\\
%\end{tabular}
%\caption{Evaluation and comparison of the proposed {\it E}nKCF tracker on the OTB100 dataset. OTB100 dataset consists of $100$ video sequences of different objects from recent literatures.}
%\label{fig:OTB100_DATASET}
%\end{figure}
%---------------------------------------------------------------------- 
\section{Conclusion} \label{sc:Conclusion}
%---------------------------------------------------------------------- 
Running a computer vision algorithm on any existing embedded systems
for real-world applications is economically and practically very
attractive. To make such pipelines more plausible, however, those
algorithms should run faster with small footprint of computation
resource consumption. To make an object tracking algorithm with these
practical requirements available, we proposed an extension of KCF that
essentially deploys three KCFs, in turn, to address the scale change
and dynamic maneuvers of a target. The way we ran three KCFs is
optimal in a sense that efficiently handled the scale change and
effectively learned the translation of the target. We also developed a
Bayes filter, particle filter, to smooth the transition between three
KCFs. In particular, the particle filter estimated the target's pixel
coordinates using information about the target's motion observed over
frames. We used two publicly available dataset to evaluate the
performance of the proposed algorithm and found, on average, the
performance of the proposed algorithm is better than those of the
existing ones over 5\% on precision at 20 pixels and 10-20\% on AUC on
average. Our implementation ran at 340 fps for OTB100 and at 416 fps
for UAV123 data that is faster than DCF (292 fps) for OTB100 and KCF
(292 fps), DCF (457 fps) for UAV123.

As future work, we investigates a way of re-initializing a target when
the target is lost, due to occlusion, illumination change, drastic
camera motion, etc.
%--------------
%\section*{Acknowledgements}
%put stuff here for the accepted , but not the ICCV version
